Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2019-05-30 papers/Visual Diagnostics of a Model Explainer/visual-diagnostics-of-a-model-explainer.Rnw
fixed typos

Machine learning models have been proven to provide accurate predictions in many areas of applications. Carriquiry et. al. (source) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forests model. Yu, Beam, and Kohane (2018) describe how machine learning has advanced healthcare in ways such as automated medical image diagnoses with neural networks and predictions of clinical outcomes with Bayesian networks. This impressive predictive ability, however, comes at a cost.

>>>>

Machine learning models have been proven to provide accurate predictions in many areas of applications. Carriquiry et al. (2019) discuss the use of pattern recognition analyses in the forensics sciences to determine whether two bullets were fired from the same gun with the use of a random forests model. Yu, Beam, and Kohane (2018) describe how machine learning has advanced healthcare in ways such as automated medical image diagnoses with neural networks and predictions of clinical outcomes with Bayesian networks. This impressive predictive ability, however, comes at a cost.
